\documentclass[10pt,letterpaper,ragged2e]{altacv}
\usepackage[letterpaper, margin=1in]{geometry}
\usepackage[utf8]{inputenc}

% Change the page layout if you need to
\geometry{left=1cm,right=11cm,marginparwidth=8.5cm,marginparsep=1cm,top=1.25cm,bottom=1.25cm}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Carlito}
\else
  % If using pdflatex:
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\begin{document}
\name{Andrew Gerstenslager}
\tagline{MS Computer Science Student | Data Science \& Robotics Engineer}
\personalinfo{%
	\phone{+1 (330)-696-3493}
	\homepage{andrewgerstenslager.com}
	\email{andrewgerstenslager@gmail.com}
	\linkedin{linkedin.com/in/andrew-gerstenslager}
	\github{github.com/AndrewGerstenslager}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
	\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[resume_right_robotics]{Education}
\cvevent{University of Cincinnati}{Master of Science - Computer Science}{Expected May 2025}{Cincinnati, OH}
\begin{itemize}
	\item GPA: 3.88
\end{itemize}

\divider

\cvevent{University of Cincinnati}{Bachelor of Science - Computer Engineering}{May 2024}{Cincinnati, OH}
\begin{itemize}
	\item GPA: 3.71 \hspace{1em}|\hspace{1em} Minor: Finance
\end{itemize}

\cvsection{Experience}

\cvevent{\textbf{Data Science \& Engineering Co-Op}}{84.51°}{August 2022 -- August 2023}{Cincinnati, OH}
\begin{itemize}
	\item \textbf{Data Science Co-Op (May 2023 -- August 2023):}
	      \begin{itemize}
		      \item Implemented a LSTM-based anomaly detection Python package using TensorFlow autoencoders.
		      \item Designed and optimized the package flow for seamless integration, while reducing GPU runtime training costs by over 80\%.
		      \item Led product owner meetings to demonstrate anomaly detection use cases for data analysis.
	      \end{itemize}
	\item \textbf{Data Engineering Co-Op (August 2022 -- December 2022):}
	      \begin{itemize}
		      \item Contributed to internal Python tools for household matching package, focusing on privacy compliance.
		      \item Rewrote internal API from Flask to FastAPI, enhancing performance and aligning with company standards.
		      \item Developed client-facing Angular features and updated Terraform configurations to update dependencies.
	      \end{itemize}
\end{itemize}

\divider

\cvevent{\textbf{Computer Engineering Co-Op}}{L3Harris Technologies}{May 2020 -- May 2022}{Cincinnati, OH}
\begin{itemize}
	\begin{itemize}
		\item Completed 4 semester-long rotations working on the test equipment team developing C\# .NET applications for circuit board testers.
		\item Devised machine learning system for manufacturing failure prediction for environmental stress tests using Scikit-learn.
		\item Migrated team's main version control from SVN to Git.
		\item Documented test equipment hardware and software using 3D models, BOMs, and Doxygen.
	\end{itemize}
\end{itemize}

\divider

\cvevent{\textbf{President - UC Robotics Team}}{}{August 2020 -- August 2022}{Cincinnati, OH}
\begin{itemize}
	\item Led a team of 20 members in designing and building autonomous robots for the Intelligent Ground Vehicle Competition (IGVC).
	\item Upgraded the robot's software from ROS1 to ROS2, enhancing performance and reliability.
	      %%\item Developed image processing pipelines using OpenCV for real-time object detection and navigation.
	      %%\item Rebuilt network architecture for remote access and field connectivity, improving operational efficiency.
	\item Managed project timelines, coordinated team efforts, and introduced agile methodologies to track progress.
	\item Currently a graduate student advisor for the team
\end{itemize}

\clearpage
\end{document}
