\cvsection{SKILLS}
\begin{itemize}
	\item\bf{AI \& Machine Learning}\normalfont{: Deep Learning, Neural Networks, Computer Vision, TensorFlow, PyTorch, Imitation Learning}
	\item\bf{Data Science}\normalfont{: Data Processing, Feature Engineering, Spark, Model Validation, Statistical Analysis}
	\item\bf{Cloud Computing}\normalfont{: Azure (SQL Server, AutoML), AWS, Docker Swarm, Kubernetes (basic)}
	\item\bf{Software Development}\normalfont{: Python, C++, Git, Docker, Node.js, CI/CD (GitHub Actions), Neovim}
	\item\bf{Tools \& Frameworks}\normalfont{: OpenCV, NumPy, Pandas, Scikit-learn, UNET, Transformer Models}
\end{itemize}

\cvsection{Research}
\cvproject{Master's Thesis: Bio-Inspired Navigation using Place Cells}
\begin{itemize}
	\item Enhanced biologically-inspired navigation models by incorporating 3D LiDAR data for improved spatial localization.
	\item Analyzed CNN autoencoders to extract spatial properties of hidden layers; exploring autoencoders as tokenizers for transformers on navigation tasks.
	\item Preparing a publication for IJCNN on 3D Boundary Vector Cells outperforming traditional 2D implementations.
\end{itemize}


\cvproject{Multi-Modal Deep Learning Fusion Network}
\begin{itemize}
	\item Designed a CNN-DNN fusion architecture for processing multi-modal data, achieving 80\% accuracy.
	\item Conducted Monte Carlo validation testing for robust model performance evaluation.
\end{itemize}

\cvsection{Projects}

\cvproject{Cloud Computing Class Project}
\begin{itemize}
	\item Designed and deployed a dynamic housing pricing model using Azure services, including SQL Server and AutoML.
	\item Built an interactive map frontend in Node.js, allowing users to input house attributes and receive price predictions.
\end{itemize}
\cvproject{Retina Vein Segmentation}
\begin{itemize}
    \item Created from scratch a U-NET image segmentation model to segment veins from images of veins in the retina
\end{itemize}
\cvproject{Transformer-Based Machine Translation Project}
\begin{itemize}
    \item Built and trained a transformer model to translate Portuguese sentences into English, achieving a BLEU score of 0.28.
    \item Preprocessed multilingual text data, including tokenization, cleaning, and sentence alignment, to create a high-quality dataset.
\end{itemize}


\cvsection{Achievements}
\begin{itemize}
	\item\bf{Best Research Presentation}\normalfont{ - 49th DCASS (2024)}
	\item\bf{First Place, Best AWS Use, Best Data Science}\normalfont{ - Revolution UC Hackathon (2024)}
	\item\bf{Imitation Learning Research}\normalfont{: Published on arXiv}
	\item\bf{Eagle Scout}\normalfont{ (2019)}
\end{itemize}